API Evolution: A Study of Software Releases and Change Trends Leading to Stability

### 2014-01-13 apie-2013/paper.tex
APIE next version done.

The remainder of this paper is laid out as follows. Section~\ref{sec:rel} goes over the related work of release study and stability. Sections~\ref{sec:meth}
explains our methodology and tools used in solving our research problem.
Section \ref{sec:results} gives a full representation of the results and trends found as well as the 9 change trends found
to be most prominent. Finally, Sections~\ref{sec:fut} and~\ref{sec:con} give our future work to follow this study and final conclusions respectively.

>>>>

The remainder of this paper is laid out as follows. Section~\ref{sec:rel} goes over the related work, Sections~\ref{sec:meth}
explains our methodology and tools used in solving our research problem,
Section \ref{sec:results} gives a full representation of the results and trends found, and Sections~\ref{sec:fut} and~\ref{sec:con} give 
our future work to follow this study and final conclusions respectively.
